Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-03-19 paper.tex
Add NSF grant to acnkowledgments

\begin{acknowledgments}
The authors acknowledge Vincent Neary and the Sandia National Laboratories Water
Power Program for use of their Red Mesa high performance computing cluster.
\end{acknowledgments}

>>>>

\begin{acknowledgments}
    The authors would acknowledge funding through a National Science Foundation
    CAREER award (principal investigator Martin Wosnik, NSF 1150797, Energy for
    Sustainability, program manager Gregory L. Rorrer). The authors also thank
    Dr. Vincent S. Neary and the Sandia National Laboratories Water Power
    Program for use of their Red Mesa high performance computing cluster.
\end{acknowledgments}
